Fast and optimal centroiding of faint stars

### 2015-01-30 ms/figure.tex
Update figure.tex

In this work, we proposed a method for centroiding stars based on fitting a low order
polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial
centroiding, 3$\times$3 quartic approximation, and PSF fitting.
In order to make this comparison, we performed some tests on a large number of
simulated data, and investigated to see if these estimators can saturate the Cramer-Rao
lower bound, or how close to they get to saturating the bound.

Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
centroid estimates that saturate the CRLB. We found that the estimates found by 3$\times$3
polynomial method are far away from saturating the CRLB. On the other hand, the RMSE of
centroid estimates of our proposed 3$\times$3 modified polynomial method, and that of the
3$\times$3 quartic approximation, are much closer to the CRLB. The performance of these two
methods however, is limited by two important factors: \emph{(i)} signal-to-noise ratio,
and \emph{(ii)} size of the stars.

>>>>

An optimal stellar centroiding algorithm must always saturate the Cramer-Rao lower 
bound. That is, in all ranges of background noise level, size, radial light profile,
and shape, it must preserve information about the centroid of stars. In practice however,
that is only achievable when we know the exact PSF. Since, we do not know the exact PSF
profile, we make use of various approximate centroiding algorithms. In this work, we
studied how different methods get close to saturating the CRLB for relatively low SNR
stars.

We also proposed a method for centroiding stars based on fitting a low order
polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial
centroiding, 3$\times$3 quartic approximation, moment-based method, and PSF fitting.
In order to make this comparison, we performed some tests on a large number of
simulated data, and investigated to see if these estimators can saturate the Cramer-Rao
lower bound, or how close to they get to saturating the bound.

Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
centroid estimates that saturate the CRLB; with the exception of SNR being less than 10, 
in which a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
from the CRLB.

We found that the estimates found by 3$\times$3 polynomial method are far away from
saturating the CRLB. On the other hand, the RMSE of centroid estimates of our proposed
3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation,
are much closer to the CRLB. The performance of these two methods however, is limited by
two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.
